Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-04-14 manuscript/sections/results.tex
add results for profile/volume effects

result: reducing peaker and flex needs
result: two effects, one stay also in clean grids

plot with e.g. germany system capacity differences
new plot in profile and volume.

>>>>

\vspace{10pt}
\begin{res}
    24/7 CFE procurement reduces system-level \co emissions via two mechanisms that can be isolated as profile and volume effects.
\end{res}

\vspace{5pt}
\begin{res}
    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies between 2025 and 2030 with a cleaner state of local grids.
\end{res}

\vspace{5pt}
\begin{res}
    24/7 procurement reduces the needs for flexibility in the rest of the system.
\end{res}

text on results 8 and 9

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Emissions reduction in a local zone by 24/7 hourly matching with 100\% target -- profile and volume effects isolated.}
        \includegraphics[width=0.95\columnwidth]{profile-volume.pdf}
        \label{fig:10-profile-volume.pdf}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Additional emissions reduction in local zone by 100\% hourly over annual matching as percentage points of reference zone emissions.}
        \includegraphics[width=0.95\columnwidth]{hourly-annual.pdf}
        \label{fig:10-hourly-annual.pdf}
    \end{subfigure}
    \caption{
        System-level emission reduction: benchmark of procument policies and isolation of decarbonisation mechanisms. 
    \cref{fig:10-profile-volume.pdf} shows breakdown of emissions reduction in a local zone if 10\% of \gls{ci} load follows 24/7 hourly CFE procurement with 100\% target. The profile are volume effects are isolated.
    \cref{fig:10-hourly-annual.pdf} shows additional emissions reduction in a local zone by 100\% hourly over annual matching.}
    \label{fig:decarbonisation_story}
\end{figure}

text on result 10

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
    \caption{
    Difference in generation capacity expansion in the whole European electricity system (including \gls{ci} resources) with and without clean energy procurement. 
    Selected scenario of Germany, 2030, technological palette~1.}
    \label{fig:10-2030-DE-p1-system_capacity_diff.pdf}
\end{figure}
